Agile Monitoring of Evolving Web Services: For the Little Man

### 2018-04-09 overhead.tex
added benchmark measurements
nicer benchmarking image
a nice table with the benchmark numbers is in

\section{Overhead of the \tool}
\label{sec:overhead}

To know the performance overhead of the \tool, we have implemented an automated benchmark system. It is open source and available online and can be tested by the reader. The benchmark does the following steps:

\begin{itemize}
	\item downloads the latest version of the Zeeguu API and installs it in a Docker container
	\item calls multiple endpoints for 500 times tracking the response times. the endpoints are called in three configurations
	\begin{itemize}
		\item with the dashboard disabled
		\item with the dashboard enabled but with the outlier detection deactivated
		\item with the dashboard enabled and the outlier tracking enabled always
	\end{itemize}
\end{itemize}

\Fref{fig:bench} shows the results of calling every one of the three endpoints for 500 times.

\begin{figure}[h!]
	\centering
	\includegraphics[width=\linewidth]{benchmark}
	\caption{The distribution of response times when calling the three endpoints for 500 times in three conditions: no dashboard, dashboard but no outliers, dashboard and always outlier routine}
	\label{fig:bench}
\end{figure}

Based on running the benchmarking script we can report

>>>>

\newpage
\section{Overhead of the \tool}
\label{sec:overhead}

To measure the performance overhead of the \tool, we have implemented an automated benchmarking system. It is open source and available online and can be tested by the reader. The benchmark downloads the latest version of the \zee API and installs it in a Docker container. Then it calls several selected endpoints for 500 times each, tracking the response times. The endpoints are called in three different configurations:

	\begin{enumerate}
		\item With the dashboard disabled
		\item With the dashboard enabled but with the outlier detection deactivated
		\item With the dashboard enabled and the outlier treshold set to zero. This helps us measure the time usually spent in an outlier.
	\end{enumerate}

\Fref{fig:bench} shows using violin plots the distribution of times resulting from running the benchmark for three different endpoints on a quad-core machine, with Intel Core i5-4590 processor, @ 3.30GHz, 8G of RAM and 240GB SSD disk drive.

\begin{figure}[h!]
	\centering
	\includegraphics[width=\linewidth]{benchmark2.pdf}
	\caption{The distribution of response times when calling the three endpoints for 500 times in three conditions: no dashboard, dashboard but no outliers, dashboard and always outlier routine}
	\label{fig:bench}
\end{figure}

\input{overhead-table}
